### 2010-12-29 docs/slides/result.tex
Analysis and application updated.

>>>>

\frame
{
	\frametitle{Analysis}
	\framesubtitle{Batesian Mimicry}

	\begin{itemize}
		\item Batesian Mimicry has taken effect, for all possible initial conditions.
			\begin{itemize}
				\item Every ring of unpalatable species there is a palatable ring.
			\end{itemize}
	\end{itemize}

	\begin{itemize}
		\item Start with palatable population, prey reaches extinction.\\
		\textbf{Reason:} No models to mimic for palatable species.
	\end{itemize}

	\begin{itemize}
		\item \textbf{Conclusion:} This model can simulate evolution of Batesian Mimicry.
	\end{itemize}

\frame
{
	\frametitle{Analysis}
	\framesubtitle{Mullerian Mimicry}

	\begin{quote}
		``Mullerian mimics converge into one large ring."
	\end{quote}

	\begin{itemize}
		\item Initialize simulation with 4 unpalatable species. No palatable ones.
		\item After 10k iteration all unpalatable species survive with dominance.
		\item \textbf{Reason:} Predator minimum memory configuration set to 4.
	\end{itemize}

	\begin{itemize}
		\item \textbf{New experiment:} reduce predator memory to 1.\\
		\item \textbf{Observation:} The phenomenon of single large ring do not occur. 
		\item \textbf{Conclusion:} Similar to Franks and Noble.\\
		Multiple Mullerian mimics do not converge into one large ring.
	\end{itemize}	
}

\frame
{
	\frametitle{Analysis}
	\framesubtitle{Conclusion}

	\begin{itemize}
		\item Successful simulation of evolution of mimicry.
		\item Accurate simulation of mimicry ring.\\
		Diverse new rings and shift in their population.
		\item Proof of the theory of Turner: evolution of mimicry with punctuated equilibrium.
	\end{itemize}
}
